---
title: "Day 02 Activity: Linear Regression"
subtitle: "SoCal Data Science Bootcamp Summer 2023"
format: 
  html:
    toc: true
    html-math-method: katex
    css: style.css
---

```{r}
#| echo: false
#| warning: false
```

In this activity you will explore the `penguins` data from the `palmerpenguins` package. Specifically, we will be interested in modeling the length of penguin flippers as a function of various predictors.

```{r message=FALSE, warning=FALSE}
library(palmerpenguins)
library(tidyverse)
library(broom)
library(janitor)
na.omit(data(penguins))

```

## Question 1
Explore and visualize the relationship between the length of penguin flippers and bill length. 

a) Fit a linear regression model for he length of penguin flippers as a function of the bill length. Interpret the parameter estimates. 

```{r}
model_g <- lm( flipper_length_mm ~ bill_length_mm , data = penguins)
tidy(model_g)

```
126.68 + 1.69

b) If a penguin has a 34.0 mm bill length, what is the predicted flipper length based on this model?
FLM = 126.68 + 1.69 x 34.0 => 184.14

c) What is the residual for the penguin with bill length of 34.0 mm?

```{r}
penguins <- penguins %>% 
  modelr::add_residuals(model_g)

ggplot(penguins, aes(x = bill_length_mm, y = resid)) +
  geom_point() +
  geom_hline(yintercept = 0)
```

d) Check to see if the conditions for fitting a linear regression model have been met. 

L: Linear

```{r}
babies %>% 
  ggplot (aes(x = gestation, y = bwt)) +
  geom_point()
```

I: Independent observations

N: Normality of residuals 

E: Equal/constant variability around the line for all values of the explanatory variable

e) Find a 95% confidence interval for the slope and interpret it. Determine if a positive or negative relationship can be concluded. 
 

## Question 2
Now that we have explored the relationship between the length of penguin flippers and bill length, let's consider adding in other potential predictors.

a) Fit a model with bill length and island as predictors.
b) Create a visual of bill length vs flipper length, including island as an additional variable. 
c) Write out the equation for the least squares regression model and interpret the parameter estimates. 
d) Check the model conditions.
